FINE SCALE REGISTRATION OF SIDEWALKS AND OTHER RIBBON-LIKE FEATURES FROM AERIAL IMAGERY

### 2018-11-18 Chapters/2.Theory/Background.tex
Made final corrections ot English and language, fixed some acronyme,      etc.

\section{\ac{CRF}} \label{sec:crf}
\acfp{CRF} are is a class of statistical graphical modeling methods that often applied in pattern recognition and machine learning~\cite{MAL-013}. 
As a type of discriminative undirected probabilistic graphical model, \acp{CRF} are commonly used for segmenting, labeling or parsing of sequential data, such as in computer vision, structure segmentation and object recognition~\cite{RuizSarmiento2015UPGMppA, 1315232, lafferty2001conditional}. 
For road segmentation, several approaches are able to locate the precise 
boundaries by treating it as a \ac{CRF} problem~\cite{ActiveContou09, Achanta:149300}.

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.85\textwidth]{Figures/GMM_needed.png}
\caption[Density Background Subtraction]{
A demonstration of the \ac{EM-GMM} algorithm on sample inputs, probability densities are shown in gray scale. 
From top to bottom, row 1 shows foreground density on a sample path, row 2 show background density on 
the same sample path as row 1. 
Row 3 and 4 show the same with a different sample path. 
A lighter color represents higher probability density.}
\label{fig:gmm_sample_1}
\end{figure}

\section{\ac{DP}}\label{sec:dp}

@@

\ac{DP} often involves first filling in a table with the \textit{optimal value} of sub-problems, and
in order to recover the sequence of decisions that led to the optimal value a process of \textit{backtracking} is used. 
\figref{fig:lcs_dp} gives a example of a famous dynamic programming problem, finding the length of the Longest Common Sequence. 
Given two strings $t_1=\langle t_{1,1}, t_{1,2}, \dots, t_{1,m}\rangle$
and $t_2=\langle t_{2,1}, t_{2,2}, \dots, t_{2,n}\rangle$, we aim to identify 
the \textit{length} of the longest subsequence that is common to both $t_1$ and $t_2$.
In this case a subproblems are prefixes of the strings $t_1$ and $t_2$.
Once we know the lengths of the longest subsequences for every subproblem, we can use 
backtracking to generate the longest subsequence itself. 
The longest common sequence is useful for geospatial processing, for example it has been use for intersection detection from GPS
traces~\cite{Xie2017DetectingRI}.

>>>>

\section{\ac{CRF}} \label{sec:crf}
\acfp{CRF} are a class of statistical graphical modeling methods that are often applied in pattern recognition and machine learning~\cite{MAL-013}. 
\acp{CRF} are commonly used for segmenting, labeling or parsing of sequential data, such as in computer vision, semantic segmentation and object recognition~\cite{RuizSarmiento2015UPGMppA, 1315232, lafferty2001conditional}. 
For road segmentation, several approaches are able to locate the precise 
boundaries by treating it as a \ac{CRF} problem~\cite{ActiveContou09, Achanta:149300}.

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.85\textwidth]{Figures/GMM_needed.png}
\caption[Density Background Subtraction]{
A demonstration of the \ac{EM-GMM} algorithm on sample inputs, probability densities are shown in gray scale. 
From top to bottom, row 1 shows foreground density on a sample path, row 2 shows background density on 
the same sample path as row 1. 
Row 3 and 4 show the same with a different sample path. 
Lighter colors represents higher probability density.}
\label{fig:gmm_sample_1}
\end{figure}

\section{Dynamic Programming}\label{sec:dp}

@@

\ac{DP} often involves first filling in a table with the \textit{optimal value} of sub-problems, and
in order to recover the sequence of decisions that led to the optimal value a process of \textit{backtracking} is used. 
\figref{fig:lcs_dp} gives a example of a famous dynamic programming problem, finding the length of the Longest Common Sequence. 
Given two strings $t_1=\langle t_{1,1}, t_{1,2}, \dots, t_{1,m}\rangle$
and $t_2=\langle t_{2,1}, t_{2,2}, \dots, t_{2,n}\rangle$, we aim to identify 
the \textit{length} of the longest subsequence that is common to both $t_1$ and $t_2$.
In this case subproblems are prefixes of the strings $t_1$ and $t_2$.
Once we know the lengths of the longest subsequences for every subproblem, we can use 
backtracking to generate the longest subsequence itself. 
The longest common sequence is useful for geospatial processing, for example it has been use for intersection detection from GPS
traces~\cite{Xie2017DetectingRI}.

### 2018-11-18 Chapters/2.Theory/Theory.tex
Made final corrections ot English and language, fixed some acronyme,      etc.

We now turn our attention to competing prior art that would seem to address the same or a similar problem to the proposed approach. 
A variety of approaches are able to locate precise object boundaries, although few directly address
the problem of sidewalk segmentation. Several tools for segmentation
appear for segmenting features in \ac{VHR}, we list Grabcut ~\cite{Rother2004-ou},
SLIC~\cite{Achanta:149300}, and Active Contours~\cite{Kass88snakes:active} as examples. 
Results for
these methods on a simple sidewalk are shown in \figref{fig:Method_comparison} which shows
qualitative results of each method. We observe that \GrabCut{} had decent performance on this example,
but it is still unable to identify edges in shadow or correctly determine the width of the sidewalk
region in the vicinity of a driveway, which seems to be made of the same material as the sidewalk.
In addition we observe that all three approaches recognize the gutter as part of the sidewalk
because it has a similar texture.

@@

\acf{SLIC} is a method for identifying super-pixels, which segment a large image into different
irregularly shaped regions of homogeneous appearance or texture~\cite{Achanta:149300}. It finds
compact evenly distributed homogeneous regions of an image as a pre-processing step, so that image
segmentation can be accomplished by grouping super-pixels which snap to natural boundaries in an
image. Alternatively, super-pixels can initiate a region growing process~\cite{Borovec2017-fz}. As
shown in figure \ref{fig:slic}, \ac{SLIC} will identify a non-sidewalk feature as positive if there
is a shadow covering the sidewalk, which may lead to over mark the boundary (\acp{FP}). 
The results we show \ac{SLIC} segmentation are superpixels that cross the original \ac{GIS} line strip.
When strong edges exist within the sidewalk (e.g. from shadows or occlusion) the \ac{SLIC} approach may
 fail to recognize part of the sidewalk (if the superpixel does not cross the line strip) or it may 
 detect objects that extend outside the sidewalk (if the superpixel crosses the line strip). 
Thus, finding a way to separate such a feature become
important. Trying to decrease the size or the width of each super-pixel is one of the ways to fix
it but may cause an incompleteness since each super-pixel is smaller than the width of the sidewalk.
So the idea of width control become necessary.

@@

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{Figures/ac1.png}
\caption[Example of Active Contours]{
Detail demonstration of the \ActiveContours{} method. 
Row 2 indicates examples of false positive, which is recognized a non-sidewalk feature 
(shadow) and similar texture (driveway) as a part of sidewalk.}
\label{fig:ac}
\end{figure}

@@

Both \ac{SLIC} and active contours start from an initial shape to find precise boundaries by solving a \ac{CRF} problem. 
In addition, graph cut are capable of global \ac{CRF} optimization in some situations, and iterative graph cut are used by the GrabCut algorithm to refine an initial segmentation~\cite{Rother2004-ou}. However in figure \ref{fig:Method_comparison} and figure \ref{fig:ac}, we show the segmentation results of these methods, and note that they struggle to constrain their results to ribbon-like shapes with smooth thickness and mid-line.
These color or boundary smoothness methods fail to capture an important quality of ribbon-like features, which is the thickness at one point depends not only its adjacent points but also its topologically distant points along the contour.

\section{\ac{CNNs}}

Another image segmentation approach that has seen extraordinary success is the use of Convolutional Neural Networks (CNNs) and transposed convolution~\cite{Badrinarayanan2017-il, Noh2015-ni, Shelhamer2017-rf, Ronneberger2015-sv}. 
Unlike the proposed approach, these have millions of tunable parameters and need significant pre-annotated data and offline training to build a model. 
In a recent exploration of learning to segment street networks from online maps~\cite{Kaiser2017-np}, built a fully convolutional network with 137 million parameters.
A similar approach with another deep architecture called U-net~\cite{Ronneberger2015-sv} was applied to the street network segmentation problem~\cite{Zhang2017-gi}.
These approaches claim to be robust to occlusion and ambiguous regions, but they benefit from a large amount of carefully annotated data that includes road width~\cite{Mnih2013-dp}. 
This type of pre-annotated data with aligned aerial imagery is much harder to obtain for walking paths. 
\ac{DPRST} has only handful of tunable parameters with clear interpretations, so that they can be interactively set and used without offline training.

>>>>

The previous section provided background; we now turn our attention to competing prior art that would seem to address the same or a similar problem to the proposed approach. 
A variety of approaches are able to locate precise object boundaries, although few directly address
the problem of sidewalk segmentation. Several tools for segmentation
appear for segmenting features in \ac{VHR}, we list Grabcut ~\cite{Rother2004-ou},
SLIC~\cite{Achanta:149300}, and Active Contours~\cite{Kass88snakes:active} as examples. 
Results for
these methods on a simple sidewalk are shown in \figref{fig:Method_comparison} which shows
qualitative results of each method. We observe that \GrabCut{} had decent performance on this example,
but it is still unable to identify edges in shadow or correctly determine the width of the sidewalk
region in the vicinity of a driveway, which seems to be made of the same material as the sidewalk.
In addition we observe that all three approaches recognize the gutter as part of the sidewalk
because it has a similar texture.

@@

\acf{SLIC} is a method for identifying super-pixels, which segment a large image into different
irregularly shaped regions of homogeneous appearance or texture~\cite{Achanta:149300}. It finds
compact evenly distributed homogeneous regions of an image as a pre-processing step, so that image
segmentation can be accomplished by grouping super-pixels which snap to natural boundaries in an
image. Alternatively, super-pixels can initiate a region growing process~\cite{Borovec2017-fz}. As
shown in figure \ref{fig:slic}, \ac{SLIC} will identify a non-sidewalk feature as positive if there
is a shadow covering the sidewalk, which may lead to over mark the boundary (\acp{FP}). 
The results we show as \ac{SLIC} segmentation are superpixels that cross the original \ac{GIS} line strip.
When strong edges exist within the sidewalk (e.g. from shadows or occlusion) the \ac{SLIC} approach may
 fail to recognize part of the sidewalk (if the superpixel does not cross the line strip) or it may 
 detect objects that extend outside the sidewalk (if the superpixel crosses the line strip). 
Thus, finding a way to separate such a feature becomes
important. Trying to decrease the size or the width of each super-pixel is one of the ways to fix
this problem, but reducing the sizes of superpixels may result in poor recall of sidewalk pixels 
since each super-pixel is smaller than the width of the sidewalk.

@@

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{Figures/ac1.png}
\caption[Example of Active Contours]{
A detailed demonstration of the \ActiveContours{} method. 
Row 2 indicates examples of false positives, which recognized a non-sidewalk feature 
(shadow) and similar texture (driveway) as a part of sidewalk.}
\label{fig:ac}
\end{figure}

@@

Both \ac{SLIC} and active contours start from an initial shape to find precise boundaries by solving a \ac{CRF} problem. 
In addition, graph cuts are capable of global \ac{CRF} optimization in some situations, and iterative graph cut are used by the GrabCut algorithm to refine an initial segmentation~\cite{Rother2004-ou}. However in figure \ref{fig:Method_comparison} and figure \ref{fig:ac}, we show the segmentation results of these methods, and note that they struggle to constrain their results to ribbon-like shapes with smooth thickness and mid-line.
These color or boundary smoothness methods fail to capture an important quality of ribbon-like features, which is the thickness at one point depends not only its adjacent points but also its topologically distant points along the contour.

\section{Convolutional Neural Networks}

Another image segmentation approach that has seen extraordinary success is the use of Convolutional Neural Networks (CNNs) and transposed convolution~\cite{Badrinarayanan2017-il, Noh2015-ni, Shelhamer2017-rf, Ronneberger2015-sv}. 
Unlike the proposed approach, these have millions of tunable parameters and need significant pre-annotated data and offline training to build a model. 
In a recent exploration of learning to segment street networks from online maps, Kaiser et al.~\cite{Kaiser2017-np} built a fully convolutional network with 137 million parameters.
A similar approach with another deep architecture called U-net~\cite{Ronneberger2015-sv} was applied to the street network segmentation problem~\cite{Zhang2017-gi}.
These approaches claim to be robust to occlusion and ambiguous regions, but they benefit from a large amount of carefully annotated data that includes road width~\cite{Mnih2013-dp}. 
This type of pre-annotated data with aligned aerial imagery is much harder to obtain for walking paths. 
The proposed \ac{DPRST} approach has only a few tunable parameters with clear interpretations, so that they can be interactively set and used without offline training.

### 2018-11-18 Chapters/3.Hypothesis/Hypothesis.tex
Made final corrections ot English and language, fixed some acronyme,      etc.

which combines the probabilities of seeing each color at offset $s$ in the ribbon image conditioned on whether the color is inside or outside of the ribbon.
However, we assume ribbons are continuous with respect to the position of their mid-line and their thickness, likelihood of the most probable path up to offset $s$ is

\begin{align}
\ribbonnll(s, j, k) &=  \begin{cases}
-\ln \Pr(k, j) & \text{if } s = 0\\
   \rownll(s, j, k){+} \\
   \hspace{1em}\displaystyle\max_{\delta_t,\delta_r} 
   \left[
   -\ln p(\delta_t{,}\delta_r){+}
   \ribbonnll(s{-}1{,}j{+}\delta_t{,}k{+}\delta_r)
 \right]
 & \text{if } s > 0.\\
\end{cases}
\end{align}

>>>>

which combines the probabilities of seeing each color at offset $s$ in the ribbon image conditioned on whether the color is inside or outside of the ribbon.
If we assume ribbons are connected with respect to the position of their mid-line and their thickness, then th likelihood of the most probable path up to offset $s$ is

\begin{align}
\ribbonnll(s, j, k) &=  \begin{cases}
-\ln \Pr(k, j) & \text{if } s = 0\\
   \rownll(s, j, k){+} \\
   \hspace{1em}\displaystyle\min_{\delta_t,\delta_r} 
   \left[
   -\ln p(\delta_t{,}\delta_r){+}
   \ribbonnll(s{-}1{,}j{+}\delta_t{,}k{+}\delta_r)
 \right]
 & \text{if } s > 0.\\
\end{cases}
\end{align}

### 2018-11-18 Chapters/3.Hypothesis/Paper.tex
Made final corrections ot English and language, fixed some acronyme,      etc.

The main steps of our approach are illustrated in \figref{fig:Apparatus}; a \ac{VHR} orthorectified image is provided by our sponsor and the approximate trajectory of a sidewalk is acquired from a \ac{GIS} such as \ac{OSM}.
Alternately, an approximate trajectory could be marked by a person to digitize the sidewalk quickly. 
The initial trajectory is re-sampled and used to warp a portion of aerial image so that the trajectory is mapped to a straight, horizontal line which we call a \textit{ribbon image}. 
We use a modest assumption that colors near the center of the ribbon image are more likely to be on a walking path in order to build a probability-density estimate for walking path materials. 
Based on the probability estimate at each pixel, we construct a single ribbon with priors that control the rate of change of thickness and direction of the ribbon. 
Finally, the boundaries are warped back onto the original reference frame. 
In this section we elaborate the process of generating a ribbon image, estimating the probability that a color belongs to the same material as a walking path, and the construction of a smooth ribbon image based on the resulting probabilities.

\begin{figure}[H]
\begin{center}
\includegraphics[width=0.8\textwidth]{Figures/diagram6.png}
\caption[Framework Overview]{Our approach adopted to predict precise boundaries for ribbon-like features. Where black line indicated a sidewalk's geometric information, and red lines shown our result for the sidewalk boundaries.
 From (a) to (f), the 6 step approach introduce 
(a) input map, 
(b)~initial trajectory, 
(c)~ribbon image generation, 
(d)~density Estimation for pixels, 
(e)~the result from our \ac{DP} solution, 
(f)~the output result.}
\label{fig:Apparatus}
\end{center}
\end{figure}

@@

We develop a way to convert the given sidewalk into a ribbon image. 
As shown in figure \ref{fig:StraightenProcess}, we use the previous outcome (A) from the last step as input and connected all coordinate points data as the mid-line for the sample sidewalk. 
Then we apply a smooth function that we created to smooth the mid-line, so the shape of mid-line fits better to the actual sidewalk shape(B). 
We generate two parallel line as offsets on each side of the mid-line with a distance of twice the average width in between. 
Ideally even the mid-line is not perfectly laying on the middle, we would still fit the whole sidewalk into the ribbon image. 
For each point on the mid-line, we connect the corresponding points on both offsets to get the movement of the sidewalk and recorded them(C, D), we generate the straightened ribbon image by using the color data from each pixel in the points set that we record earlier(E). 
The image data in between each offset, with constant image width could be retrieved after that (F).
Then we reshape the image data to generate the ribbon image(G). 
Figure \ref{fig:Sample_Sidewalk_2} shows the complete ribbon-image output result on sample sidewalk. We separate it into parts to show better detail.

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{Figures/straghten.pdf}
    \caption[Ribbon Image Generation]{Ribbon image generating process: from sub-figures A to G, we showed the step by step process to generate ribbon-image from a partial sidewalk. From raw input (A), we smoothed mid line and generated parallel off-site (B). Generated pixels (C) and connected each pixel to its correspond color data from the raw input (D). After gathered pixel data (E), we removed mid-line (F) and generated the ribbon image(G).}
    \label{fig:StraightenProcess}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.95\textwidth]{Figures/sample2_demo.png}
    \caption[Sample Sidewalk 2]{A ribbon image straighten output on sample sidewalk, row 1 shows the original input, row 2 to 5 show the ribbon image output separate into parts.}
    \label{fig:Sample_Sidewalk_2}
\end{figure}

@@

We take $\RibbonImage{}$ as an input ribbon image with $m$ rows and $n=2\MaxDistance+1$ columns; $\RibbonImage{}{[i,j]}$ is a pixel in the image. 
We have an estimate $\Pr(R|\RibbonImage{}_{[i,j]}, \theta)$ which we abbreviate as $p_{[i,j]}$. 
In addition there is some small set of allowed perturbations $\delta=\{(\delta_j, \delta_k)\}$ where $\delta_j$ is a change in direction and $\delta_k$ is a change in the radius of the ribbon. 
Each perturbation has a probability $\Pr(\delta_j, \delta_k)$ that controls the shape of the curve; in our experiments we use $\delta_j\in\{-1,0,1\}, \delta_k\in\{-1, 0,1\}$ in order to ensure that results are connected, and  $\Pr(\delta_j, \delta_k)=\Pr(|\delta_j|)\Pr(\delta_k)$ is two independent multinomial distributions which require only three parameters due to symmetry and because probabilities sum to unity. 
We can interpret $c_\mathit{bend}=-\lg \Pr(\delta_j=\pm1)$ as a penalty for bending the curve, and $c_\mathit{shrink}=-\lg \Pr(\delta_k=-1)$ as a penalty for shrinking the radius, or $c_\mathit{expand} = -\lg \Pr(\delta_k=1)$ as a penalty for expanding the radius of the curve.

@@

We visualize the problem of finding a ribbon as one of choosing a three-dimensional path through a scale-space where the first two dimensions represent locations of the ribbon's center, and the third dimension represent the thickness of the ribbon as illustrated in \figref{fig:ribbon_3d}. Every ribbon must start at one end of the image and follow a three-dimensional path through scale-space to reach the other end one slice at a time. Each slice corresponds to a row of the ribbon image and a point at location $(j, k)$ in the slice partitions the row into negative regions $(0\twodots{}j-k-1)$ and $(j+k+1\twodots{}n)$ with a positive region at $(j-k \twodots{} j+k)$ with thickness $2k+1$. The likelihood of any location $(j, k)$ is the product of the probabilities that each pixel on the same row belongs to the corresponding positive or negative regions.  In fact the probability is exponentially related to the size of each pixel; if one were to increase the resolution by a factor of $r$ then the contribution of each pixel would be raised to the power of $\frac{1}{r}$ so that the product would stay constant. In order to make our parameters invariant to scale, we divide the \ac{NLL} by $\MaxDistance{}$ when estimating the likelihood of a given $(j,k)$.

@@

The pseudocode can be interpreted as follows: Line \ref{li:loop-slices} iterates through each slice of the ribbon image. Line \ref{li:loop-radius} iterates through all possible radii and line \ref{li:loop-center} explores all possible ribbon-centers from left to right. We use a variable $s$ to calculate \ac{NLL} of a set of regions as the ribbon shifts from left to right. If this is not the first slice, then line \ref{li:min-from-pred} selects the least-expensive (most probable) path that leads to location $(i, j, k)$ in the scale space.  At each step on pixel toggles from negative to positive, and one toggles from positive to negative as $s$ is updated in line \ref{li:update-s}.  We return the costs as well as the final offset and scale $(j^*, k^*)$ of the best path.

@@

Figure \ref{fig:penalty} shows our algorithm managed to separate the driveway and sidewalk under the same feature as penalty increase. So we could apply the dynamic programming solution to locate the precise boundaries of given ribbon image. The penalty control improved our performance significantly. Because of this, our approach could predict the sidewalk under the tree shadow and other shadows or obstacles, which bring us more accurate result compare to other methods.
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{Figures/penalty.png}
    \caption[Penalty Process]{Comparison with penalty change, we tested a variety of variables to decide which variable had best performance for width control. With the penalty increased at a reasonable amount, our algorithm decided not to recognize a driveway as sidewalk walk, in order to keep the sidewalk width consistent, even though they are the same texture.}
    \label{fig:penalty}
\end{figure}

As shown in figure \ref{fig:sample_result2}, after we generate the result on ribbon image, just need to simply covert the ribbon image back to its original shape by reverse the method that generates the ribbon image.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.95\textwidth]{Figures/sample2_result.png}
    \caption[Desire Output on Sample Sidewalk]{Detail demonstration on desire result after applying our dynamic programming approach. Where row 1 shows the result after reshape, row 2 to 5 shows the boundaries we calculated on ribbon image from \ref{fig:Sample_Sidewalk_2}.}
    \label{fig:sample_result2}
\end{figure}

>>>>

The main steps of our approach are illustrated in \figref{fig:Apparatus};
 a \ac{VHR} orthorectified image is provided 
 and the approximate trajectory of a sidewalk is acquired from a \ac{GIS} such as \ac{OSM}.
Alternately, an approximate trajectory could be marked by a person to digitize the sidewalk quickly. 
The initial trajectory is re-sampled and used to warp a portion of aerial image so that the trajectory is mapped to a straight, horizontal line which we call a \textit{ribbon image}. 
We use a modest assumption that colors near the center of the ribbon image are more likely to be on a walking path in order to build a probability-density estimate for walking path materials. 
Based on the probability estimate at each pixel, we construct a single ribbon with priors that control the rate of change of thickness and direction of the ribbon. 
Finally, the boundaries are warped back onto the original reference frame. 
In this section we elaborate the process of generating a ribbon image, estimating the probability that a color belongs to the same material as a walking path, and the construction of a smooth ribbon image based on the resulting probabilities.

\begin{figure}[H]
\begin{center}
\includegraphics[width=0.8\textwidth]{Figures/diagram6.png}
\caption[Framework Overview]{Our approach adopted to predict precise boundaries for ribbon-like features. 
Where a black line indicates a sidewalk's geometric information provided as input,
 and red lines shown our result for the sidewalk boundaries.
  From (a) to (f), the 6 step approach introduce 
(a) input map, 
(b)~initial trajectory, 
(c)~ribbon image generation, 
(d)~density Estimation for pixels, 
(e)~the result from our \ac{DP} solution, 
(f)~the output result.}
\label{fig:Apparatus}
\end{center}
\end{figure}

@@

We develop a way to convert the given sidewalk into a ribbon image. 
As shown in figure~\ref{fig:StraightenProcess}, we use the input image (\figurename{}\ref{fig:StraightenProcess}~A) 
and connected all coordinate points data as the mid-line for the sample sidewalk. 
Then we resample the curve at our desired output resulition (one pixel between each point) 
and apply a Laplacian smoothing function create a smooth the mid-line, so the shape of 
midline fits better to the actual sidewalk shape (\figurename{}\ref{fig:StraightenProcess}~B). 
We generate two parallel line as offsets on each side of the mid-line with a distance of twice 
our expected maximum thickness of a sidewalk. 
Ideally even if the mid-line is not perfectly centered on a walking path, we would 
still fit the whole sidewalk into the ribbon image. 
For each point on the mid-line, we connect the corresponding points on both offsets to get 
a cross-section of the sidewalk and then sample each cross section to form a lattice 
of points (\figurename{}\ref{fig:StraightenProcess}~C,D),
we generate the straightened ribbon image by using the color data from each pixel in 
the points set that we record earlier(\figurename{}\ref{fig:StraightenProcess}~E,F).
We show the resulting grid of color values that result sampling a ribbon in \figurename{}\ref{fig:StraightenProcess}~G.
Figure \ref{fig:Sample_Sidewalk_2} shows the complete ribbon-image output result on sample sidewalk. We separate it into parts to show better detail.

Note that warping the input image to form the ribbon image does not necessarily need to be done; 
the colors can be read from the raw image as needed to implement 
our algorithm. However the implementation of our dynamic programming solution
is simpler is we assume our input is a warped image $\RibbonImage{}$
derived from raw input $\InputImage{}$ using the process described above.

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{Figures/straghten.pdf}
    \caption[Ribbon Image Generation]{
    Ribbon image generating process: 
    from sub-figures A to G, 
    we show the step by step process to generate ribbon-image 
    from a partial sidewalk.
     From raw input (A), we smooth the mid-line and generate parallel offset (B). 
     Generated pixels (C) and connected each pixel to its correspond color data 
     from the raw input (D). 
     After gathering pixel data (E,F) we generate the ribbon image(G).}
    \label{fig:StraightenProcess}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.95\textwidth]{Figures/sample2_demo.png}
    \caption[Sample Sidewalk 2]{
    A ribbon image of a sample sidewalk, 
    row 1 shows the original input, 
    rows 2 to 5 show the ribbon image output separated into parts to fit on the page.}
    \label{fig:Sample_Sidewalk_2}
\end{figure}

@@

We take $\RibbonImage{}$ as an input ribbon image with $m$ rows and $n=2\MaxDistance+1$ columns;
 $\RibbonImage{}{[i,j]}$ is a pixel in the image. 
We have an estimate $\Pr(R|\RibbonImage{}{[i,j]}, \theta)$ which we abbreviate as $p_{[i,j]}$. 
In addition there is some small set of allowed perturbations 
$\delta=\{(\delta_j, \delta_k)\}$ where $\delta_j$ is a change in direction 
and $\delta_k$ is a change in the radius of the ribbon. 
Each perturbation has a probability $\Pr(\delta_j, \delta_k)$ that controls 
the shape of the curve; in our experiments we use $\delta_j\in\{-1,0,1\}, \delta_k\in\{-1, 0,1\}$ in order 
to ensure that results are connected, and  $\Pr(\delta_j, \delta_k)=\Pr(|\delta_j|)\Pr(\delta_k)$ is 
two independent multinomial distributions which require only three parameters due to symmetry 
and because probabilities sum to one. 
We can interpret $c_\mathit{bend}=-\lg \Pr(\delta_j=\pm1)$ as a penalty for bending the 
curve, and $c_\mathit{shrink}=-\lg \Pr(\delta_k=-1)$ as a penalty for shrinking the radius,
 or $c_\mathit{expand} = -\lg \Pr(\delta_k=1)$ as a penalty for expanding the radius of the curve.

@@

We visualize the problem of finding a ribbon as one of choosing a three-dimensional path through a
scale-space where the first two dimensions represent locations of the ribbon's center, and the third
dimension represent the thickness of the ribbon as illustrated in \figref{fig:ribbon_3d}. Every
ribbon must start at one end of the image and follow a three-dimensional path through scale-space to
reach the other end, one slice at a time. Each slice corresponds to a row of the ribbon image and a
point at location $(j, k)$ in the slice partitions the row into negative regions
$(0\twodots{}j-k-1)$ and $(j+k+1\twodots{}n)$ with a positive region at $(j-k \twodots{} j+k)$ with
thickness $2k+1$. The likelihood of a ribbon centered at any location $(j, k)$ of row $i$ is the product of the probabilities that
each pixel on the same row belongs to the corresponding positive or negative regions.  In fact the
probability is exponentially related to the size of each pixel; if one were to increase the
resolution by a factor of $r$ then the contribution of each pixel would be raised to the power of
$\frac{1}{r}$ so that the product would stay constant. In order to make our parameters invariant to
scale, we divide the \ac{NLL} by $\MaxDistance{}$ when estimating the likelihood of a given $(j,k)$.

@@

The pseudocode can be interpreted as follows: Line \ref{li:loop-slices} iterates through each slice
of the ribbon image. Line \ref{li:loop-radius} iterates through all possible radii and line
\ref{li:loop-center} explores all possible ribbon-centers from left to right. We use a variable $s$
to calculate \ac{NLL} of a set of regions as the ribbon shifts from left to right. If this is not
the first slice, then line \ref{li:min-from-pred} selects the least-expensive (most probable) path
that leads to location $(i, j, k)$ in the scale space.  At each step one pixel toggles from negative
to positive, and one toggles from positive to negative as $s$ is updated in line \ref{li:update-s}. 
We return the costs as well as the final offset and scale $(j^*, k^*)$ of the best path.

@@

Figure \ref{fig:penalty} shows our algorithm managed to separate the driveway and sidewalk under the same feature as penalty increase. So we could apply the dynamic programming solution to locate the precise boundaries of given ribbon image. The penalty control improved our performance significantly. Because of this, our approach could predict the sidewalk under the tree shadow and other shadows or obstacles, which bring us more accurate result compare to other methods.
\begin{figure}[H]
    \centering \includegraphics[width=\textwidth]{Figures/penalty.png} \caption[Penalty
    Process]{Comparison with penalty change, we tested a variety of variables to decide which
    variable had best performance for width control. With the penalty increased sufficiently,
     our algorithm bypasses the sidewalk in order to keep the thickness of the
    sidewalk width consistent, even though the sidewalk and driveway are the same texture.} \label{fig:penalty}
\end{figure}

As shown in figure \ref{fig:sample_result2}, after we generate the result on ribbon image, just need
to simply convert the ribbon image back to its original shape by reversing the method that generated
the ribbon image.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.95\textwidth]{Figures/sample2_result.png}
    \caption[Output on a Sample Sidewalk]{
    Detailed demonstration of the result after applying our dynamic programming approach.
     Where row 1 shows the result after reshape, rows 2 to 5 show the boundaries 
     we calculated on the ribbon image from \ref{fig:Sample_Sidewalk_2}.}
    \label{fig:sample_result2}
\end{figure}

### 2018-11-18 Chapters/4.Expect_results/Results.tex
Made final corrections ot English and language, fixed some acronyme,      etc.

We compare our results against common segmentation approaches 
\ac{SLIC}~\cite{Achanta:149300}, \ActiveContours{}~\cite{ActiveContou09} and \GrabCut{}~\cite{Rother2004-ou} 
in Table~\ref{tab:quantitative-against-common} using a manually annotated region of 
Phoenix AZ. The test region was acquired as \ac{VHR} 4-inch aerial orthophotos, 
and manually annotated by drawing a polygonal outline. 
When a portion of the sidewalk was occluded or camouflage with the surrounding pavement 
(including gutters) we used our best judgment to connect the visible portions of the sidewalk. For all of of the examples we present, with figure \ref{fig:change_on_recall} that shows detail parameters evaluations, we set $c_\mathit{bend}=\frac{1}{2}, c_\mathit{shrink}=c_\mathit{expand}=2$ which were experimentally found to produce the best result. Note that in our implementation we did not take care to ensure that $\Pr(\delta_k)$ summed to unity, and instead assumed that $-\lg \Pr(\delta_k=0)$ was zero, which does not have a probabilistic interpretation but is more convenient for computation.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.65\textwidth]{Figures/prf.png}
    \caption[Parameters Evaluation]{Detail comparison on $c_{bend}$, $c_{shrink}$ and $c_{expand}$. Where red line represent Recall, green line represent Precision and blue line represent F1. We generate these based on equations from Recall (6.2), Precision (6.1), F1 (6.3).}
    \label{fig:change_on_recall}
\end{figure}

>>>>

We compare our results against common segmentation approaches \ac{SLIC}~\cite{Achanta:149300},
\ActiveContours{}~\cite{ActiveContou09} and \GrabCut{}~\cite{Rother2004-ou} in
Table~\ref{tab:quantitative-against-common} using a manually annotated region of Phoenix AZ. The
test region was acquired as \ac{VHR} 4-inch aerial orthophotos, and manually annotated by drawing a
polygonal outline. When a portion of the sidewalk was occluded or camouflage with the surrounding
pavement (including gutters) we used our best judgment to connect the visible portions of the
sidewalk. For all of of the examples we present we set $c_\mathit{bend}=\frac{1}{2},
c_\mathit{shrink}=c_\mathit{expand}=2$ which were experimentally found to produce the best result. 
Figure \ref{fig:change_on_recall} that shows detailed parameter evaluation for
 $c_\mathit{bend},c_\mathit{shrink}$, and $c_\mathit{expand}$. 
Note that in our implementation we did not take care to ensure that $\Pr(\delta_k)$ summed to unity,
and instead assumed that $-\lg \Pr(\delta_k=0)$ was zero, which does not have a probabilistic
interpretation but is more convenient for computation.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.65\textwidth]{Figures/prf.png}
    \caption[Parameters Evaluation]{Detail comparison on $c_{bend}$, $c_{shrink}$ and $c_{expand}$.
     Where red lines represent Recall, green lines represent Precision and blue lines represent F1.}
    \label{fig:change_on_recall}
\end{figure}
